Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-30 article.tex
normalized weights

Filters $f_1$ and $f_2$ display similar performances and thus were given similar
weights (i.e., resp. $1$ and $0.9$). Additionally, these weights were chosen equal as the weights selected for the simplified method. In contrast, filters $f_3$
and $f_4$ turn out to be individually less competitive and were therefore given
smaller weights in the tuned averaging (i.e., resp. $0.01$ and $0.7$). Yet, as further shown in
Section~\ref{sapp:results}, combining all $4$ filters proves to slightly
improve performance with respect to using $f_1$ and $f_2$ only.

>>>>

Filters $f_1$ and $f_2$ display similar performances and thus were given similar
weights (i.e., resp. $0.383$ and $0.345$). These weights were chosen equal as the weights selected for the simplified method. In contrast, filters $f_3$
and $f_4$ turn out to be individually less competitive and were therefore given
smaller importance in the weighted average (i.e., resp. $0.004$ and $0.268$). Yet, as further shown in
Section~\ref{sapp:results}, combining all $4$ filters proves to slightly
improve performance with respect to using $f_1$ and $f_2$ only.
